---
title: "Capstone"
author: "AM"
date: "1/17/2019"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##R Markdown
The goal of this project is just to display that you've gotten used to working with the data and that you are on track to create your prediction algorithm. Please submit a report on R Pubs (http://rpubs.com/) that explains your exploratory analysis and your goals for the eventual app and algorithm. This document should be concise and explain only the major features of the data you have identified and briefly summarize your plans for creating the prediction algorithm and Shiny app in a way that would be understandable to a non-data scientist manager. You should make use of tables and plots to illustrate important summaries of the data set. The motivation for this project is to: 1. Demonstrate that you've downloaded the data and have successfully loaded it in.2. Create a basic report of summary statistics about the data sets.3. Report any interesting findings that you amassed so far.4. Get feedback on your plans for creating a prediction algorithm and Shiny app.

#Downloading and Unzipping Data
```{r}
if (!file.exists("./data/final")) {
  if (!file.exists("./data/Coursera-SwiftKey.zip")) {
    download.file("https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip",
                  destfile = "Coursera-SwiftKey.zip", quiet=TRUE)
  }
  
  unzip("Coursera-SwiftKey.zip", exdir = "./data");
}
```

#Loading the Data 
```{r}
En_US_blogs_text <- readLines("./data/final/en_US/en_US.blogs.txt", encoding = "UTF-8", skipNul=TRUE)
En_Twit_text <-  readLines("./data/final/en_US/en_US.twitter.txt", encoding = "UTF-8", skipNul=TRUE)
con <- file("./data/final/en_US/en_US.news.txt", open="rb")
En_US_NEWS_text <- readLines(con, encoding="UTF-8", skipNul=TRUE)
close(con)
rm(con)
```

#Summarise stats details

```{r}
file_stat<- function(text_file, lines) {
    f_size <- file.info(text_file)[1]/1024^2
    nchars <- lapply(lines, nchar)
    maxchars <- which.max(nchars)
    word_count <- sum(sapply(strsplit(lines, "\\s+"), length))
    return(c(text_file, format(round(as.double(f_size), 2), nsmall=2), length(lines),maxchars, word_count))
}

    En_US_news_stat<- file_stat("en_US.news.txt", En_US_NEWS_text)
    En_US_blogs_stat <- file_stat("en_US.blogs.txt", En_US_blogs_text)
    En_Twit_text_stat<- file_stat("en_US.twitter.txt", En_Twit_text)

    test_summary <- c(En_US_news_stat, En_US_blogs_stat,En_Twit_text_stat)

    df <- data.frame(matrix(unlist(test_summary), nrow=3, byrow=T))
    colnames(df) <- c("Text_file", "Size(MB)", "Line_Count", "Max Line Length", "Words_Count")
    print(df)
```
    
#Exploratory data analysis

#Bar Chart of High frequency words    

```{r}
require(tm)
require(ggplot2)

make_Corpus<- function(test_file) {
    gen_corp<- paste(test_file, collapse=" ")
    gen_corp <- VectorSource(gen_corp)
    gen_corp <- Corpus(gen_corp)
}
    
clean_corp <- function(corp_data) {

    corp_data <- tm_map(corp_data, removeNumbers)
 
    corp_data <- tm_map(corp_data, removePunctuation)
    corp_data <- tm_map(corp_data, stripWhitespace)
    
   
    return (corp_data)
}

high_freq_words <- function (corp_data) {
    term_sparse <- DocumentTermMatrix(corp_data)
    term_matrix <- as.matrix(term_sparse)   ## convert our term-document-matrix into a normal matrix
    freq_words <- colSums(term_matrix)
    freq_words <- as.data.frame(sort(freq_words, decreasing=TRUE))
    freq_words$word <- rownames(freq_words)
    colnames(freq_words) <- c("Frequency","word")
    return (freq_words)
}

    En_US_NEWS_text1<-sample(En_US_NEWS_text, round(0.1*length(En_US_NEWS_text)), replace = F)
    US_news_corpus <- make_Corpus(En_US_NEWS_text1)
    US_news_corpus <- clean_corp(US_news_corpus)
```
    
```{r}
US_news_most_used_word <- high_freq_words(US_news_corpus)
    US_news_most_used_word1<- US_news_most_used_word[1:15,]

    p<-ggplot(data=US_news_most_used_word1, aes(x=reorder(word,Frequency), y=Frequency,
                    fill=factor(reorder(word,-Frequency))))+ geom_bar(stat="identity") 
    p + xlab("Word") +labs(title = "Most Frequent words : US News") +theme(legend.title=element_blank()) + coord_flip()
```
    
```{r}
    En_US_blogs_text1<-sample(En_US_blogs_text, round(0.1*length(En_US_blogs_text)), replace = F)
    US_blogs_corpus <- make_Corpus(En_US_blogs_text1)
    US_blogs_corpus <- clean_corp(US_blogs_corpus)
```
    
```{r}
    US_blogs_most_used_word <- high_freq_words(US_blogs_corpus)
    US_blogs_most_used_word1<- US_blogs_most_used_word[1:15,]

    p<-ggplot(data=US_blogs_most_used_word1, aes(x=reorder(word,Frequency), y=Frequency,
                    fill=factor(reorder(word,-Frequency))))+ geom_bar(stat="identity") 
    p + xlab("Word") +labs(title = "Most Frequent words : US blogs") +theme(legend.title=element_blank()) + coord_flip()
```
    
```{r}
    {En_Twit_text1<-sample(En_Twit_text, round(0.1*length(En_Twit_text)), replace = F)
    twitter_corpus <- make_Corpus(En_Twit_text1)
    twitter_corpus <- clean_corp(twitter_corpus)}
```
    
    
```{r}
    twitter_most_used_word <- high_freq_words(twitter_corpus)
    twitter_most_used_word1<- twitter_most_used_word[1:15,]
    
    p<-ggplot(data=twitter_most_used_word1, aes(x=reorder(word,Frequency), y=Frequency,
                    fill=factor(reorder(word,-Frequency))))+ geom_bar(stat="identity") 
    p + xlab("Word") +labs(title = "Most Frequent words : Twitter") +theme(legend.title=element_blank()) + coord_flip()
```
    
```{r}
    require("wordcloud")
```

#Word Clouds

```{r}
    wordcloud(US_news_most_used_word$word[1:100], US_news_most_used_word$Frequency[1:100],
              colors=brewer.pal(8, "Dark2"))
```
    
```{r}
wordcloud(twitter_most_used_word$word[1:100], twitter_most_used_word$Frequency[1:100],
              colors=brewer.pal(8, "Dark2"))
```

